The title

### 2022-11-01 paper/manuscript.Rmd
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We manipulated the implementation of articulation and dynamics in the piece to create four types of artificial recordings. These recordings were supposed to be the reflection of students' skill levels. In one quarter of the recordings, both articulation and dynamics were implemented
[SUMMARY].
We found that 
Limitation

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We created artificial recordings to manipulate the skill levels by modifying the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music.

We found that expert pianists did not modulate their tempo depending on the skill levels of students. Compared with the tempo of the baseline performance, they did not change the tempo either. These findings indicated that tempo is not employed specifically for teaching because tempo itself is relevant to neither articulation nor dynamics. In music performance, it is possible that changing tempo might give another interpretation of music (e.g., expressive timing).

For KOT, expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was not implemented in the recordings. However, we did not find the same results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings. These findings suggest that participants modulated the articulation-related aspect of performances only.

There are two potential reasons that participants modulated articulation only for teaching purposes. One possibility would be that articulation was more important for the piece or the piece itself invites some implementations of articulation. In our previous experiment, we found that even during measuring the baseline performance before the experiment, many participants tend to implement some articulation even though nothing was notated on the sheet music (see details: Supplementary Material). To make the implementation of articulation clear, we particularly selected detached performances for the recordings where articulation was missing. Another possibility is that dynamics implementation was not perceived by participants, therefore they did not modulate the dynamic-related aspect of performances for teaching.

One of the limitations of the current study is that ---.

Future research should investigate.

Limitation

### 2022-11-01 paper/manuscript.tex
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We manipulated the implementation of articulation and dynamics in the piece to create four types of artificial recordings. These recordings were supposed to be the reflection of students' skill levels. In one quarter of the recordings, both articulation and dynamics were implemented
{[}SUMMARY{]}.
We found that
Limitation

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the skill levels of students. We created artificial recordings to manipulate the skill levels by modifying the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music.

We found that expert pianists did not modulate their tempo depending on the skill levels of students. Compared with the tempo of the baseline performance, they did not change the tempo either. These findings indicated that tempo is not employed specifically for teaching because tempo itself is relevant to neither articulation nor dynamics. In music performance, it is possible that changing tempo might give another interpretation of music (e.g., expressive timing).

For KOT, expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was not implemented in the recordings. However, we did not find the same results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings. These findings suggest that participants modulated the articulation-related aspect of performances only.

There are two potential reasons that participants modulated articulation only for teaching purposes. One possibility would be that articulation was more important for the piece or the piece itself invites some implementations of articulation. In our previous experiment, we found that even during measuring the baseline performance before the experiment, many participants tend to implement some articulation even though nothing was notated on the sheet music (see details: Supplementary Material). To make the implementation of articulation clear, we particularly selected detached performances for the recordings where articulation was missing. Another possibility is that dynamics implementation was not perceived by participants, therefore they did not modulate the dynamic-related aspect of performances for teaching.

One of the limitations of the current study is that ---.

Future research should investigate.

Limitation
